Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-07-24 writeups/dissertation/dissertation.tex
foo

\abstract{
  This research aims to develop and compare tag-recommendation models for users choosing hashtags when composing a tweet on Twitter and choosing tags when asking a question on the StackOverflow site.
  Two state-of-the-art cognitively-plausible memory models will be evaluated on how accurate they predict a user's chosen tags: an ACT-R inspired Bayesian model and a random-permutation vector-based model.
  Experiments are designed to [1] discover the best way to leverage a user's prior hashtag use as a future predictor, [2] improve the models so that each model's strengths are incorporated into the other,
  and [3] formally evaluate and compare each model's performance when recommending hashtags on Twitter and tags on StackOverflow.
  The user-customized tag-recommendation models developed with this research should be immediately useful as foundations for tag-recommendation systems on the popular Twitter and StackOverflow social media sites.
  Further, the planned performance modifications to the two memory models are aimed at the architectural level of each model.
  If these architectural modifications to two cognitively-plausible memory models significantly improve performance,
  they may suggest task-independent general modifications that can help improve model fit to human data in a much wider range of domains.
}

@@

The original plot shows the size of the spikes when high-frequency words are removed.
The entropy plot shows how the size decreases by more than an order of magnitude when the entropy weighting measure is used.
The cutoff was chosen such that the frequency plot looks similar to the entropy plot, with spikes around the same size.
Note that using a previously-defined stoplist does not remove some of the remaining high-frequency words in these datasets, which hints that this method may not be ideal when model accuracy is examined.
The cutoff that produced the frequency plot is where a word represents more than \num{.04}\% of total occurrences in the dataset.
This may or may not be equal to the value for \textcite{Sahlgren2008}, since that number was expressed in total observations (not as a percentage), and the total number of words in the dataset was not given.

>>>>

\abstract{
  The growth of social media and user-created content on online sites provides unique opportunities to study models of declarative memory.
  The task of choosing a hashtag for a tweet and tagging a post on StackOverflow was framed as a declarative memory retrieval problem.
  Millions of posts and tweets were collected, and two declarative memory models were used to predict hashtags and tags that users choose on Twitter and StackOverflow.
  Two state-of-the-art cognitively-plausible memory models were evaluated on how accurate they predict a user's chosen tags: an ACT-R inspired Bayesian model and a random-permutation vector-based model.
  The results show that past user behavior of tag use is a strong predictor of future performance, and this past behavior was successfully incorporated into the random-permutation model that previously used only context.
  Also, the common natural-language processing method to attenuate low-predictor words in the dataset was linked to ACT-R's attentional weight term,
  and an entropy-weighting technique was developed that improved model accuracy by more efficiently allocating limited attentional resources to the predictive words in the posts and tweets.
  Word order was not found to be strong predictor of tag use, and the random-permutation model performed comparable to the Bayesian model without including word order,
  which shows that the strength of the random-permutation model is not in the ability to represent word order, but rather in the way in which context information is successfully compressed.
  The results of the large-scale exploration show how the architecture of the two memory models can be modified to significantly improve accuracy,
  and may suggest task-independent general modifications that can help improve model fit to human data in a much wider range of domains.
}

@@

The original plot shows the size of the spikes when high-frequency words are removed.
The entropy plot shows how the size decreases by more than an order of magnitude when the entropy weighting measure is used.
The cutoff for the frequency plot was chosen such that the plot looks similar to the entropy plot, with spikes around the same size.
Note that using a previously-defined stoplist does not remove some of the remaining high-frequency words in these datasets, which hints that this method may not be ideal when model accuracy is examined.
The cutoff that produced the frequency plot is where a word represents more than \num{.04}\% of total occurrences in the dataset.
This may or may not be equal to the value for \textcite{Sahlgren2008}, since that number was expressed in total observations (not as a percentage), and the total number of words in the dataset was not given.
